---
title: "Creating Dummy Variables"
author: "Emily Blue"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
```

```{r code-chunk-label}

All_Crime_1 <- All_Crime_1 %>%
select(USSCIDN, OFFGUIDE, SENSPCAP, MONSEX, SENTYR, AGE, CIRCDIST, NEWEDUC, NEWRACE, WEAPON, SENTRNGE, NEWCNVTN, NEWCIT, QUARTER, SENTMON, PRESENT, SENTIMP, NUMDEPEN, CRIMHIST, CRIMPTS, XCRHISSR, XFOLSOR, GLMIN, NOCOUNTS, Region, Dependents, Race, Education, Custody_Status, Convicted, Offense, PRISDUM, SENTTCAP)

# Removing places outside of US
All_Crime_1 <- All_Crime_1 %>%
  filter(CIRCDIST != 69 & CIRCDIST != 74 & CIRCDIST != 5 & CIRCDIST != 18)
# Goes from 613411 obs to 602656

## Removing non-Citizens

All_Crime_1 <- All_Crime_1 %>%
  filter(NEWCIT == 0)
# Goes from 602656 to 325455

# Removing people under 18
All_Crime_1 <- All_Crime_1 %>%
  filter(AGE >= 18)
# From 325455 to 352346

```



### Creating a dataset with binary variables 

```{r}

########################### Race Dummy

All_Crime_1$White <- ifelse(All_Crime_1$NEWRACE == 1, 1, 0)

All_Crime_1$Black <- ifelse(All_Crime_1$NEWRACE == 2, 1, 0)

All_Crime_1$Hispanic <- ifelse(All_Crime_1$NEWRACE == 3, 1, 0)

All_Crime_1$Other <- ifelse(All_Crime_1$NEWRACE == 6, 1, 0)

########################### Education Dummy

All_Crime_1$LessthanHS <- ifelse(All_Crime_1$NEWEDUC == 1, 1, 0)

All_Crime_1$HSgrad <- ifelse(All_Crime_1$NEWEDUC == 3, 1, 0)

All_Crime_1$SomeCollege <- ifelse(All_Crime_1$NEWEDUC == 5, 1, 0)

All_Crime_1$CollegeGrad <- ifelse(All_Crime_1$NEWEDUC == 6, 1, 0)

##########################  Region Dummy

table(All_Crime_1$Region)

# Northeast
All_Crime_1$Northeast <- ifelse(All_Crime_1$Region == "Northeast", 1, 0)

table(All_Crime_1$Northeast)

# West
All_Crime_1$West <- ifelse(All_Crime_1$Region == "West", 1, 0)

table(All_Crime_1$West)

#Midwest
All_Crime_1$Midwest <- ifelse(All_Crime_1$Region == "Midwest", 1, 0)

table(All_Crime_1$Midwest)

#South

All_Crime_1$South <- ifelse(All_Crime_1$Region == "South", 1, 0)

table(All_Crime_1$South)

#################### Plea or Bail

All_Crime_1$Plea <- ifelse(All_Crime_1$NEWCNVTN == 0,1,0)

table(All_Crime_1$NEWCNVTN)
table(All_Crime_1$Plea)



####### Custody Status

All_Crime_1$Custody <- ifelse(All_Crime_1$PRESENT == "1", 1, 0)

All_Crime_1$Bail_Bond <- ifelse(All_Crime_1$PRESENT == "2", 1, 0)

All_Crime_1$Released  <- ifelse(All_Crime_1$PRESENT == "3", 1, 0)

All_Crime_1$Other_Status <- ifelse(All_Crime_1$PRESENT == "4", 1, 0)


table(All_Crime_1$PRESENT)

table(All_Crime_1$Bail)
table(All_Crime_1$Custody)
table(All_Crime_1$Released)
table(All_Crime_1$Other_Status)


######## Renaming some vars

All_Crime_1 <- All_Crime_1 %>%
rename(OffenseLevel = XFOLSOR)

All_Crime_1 <- All_Crime_1 %>%
rename(CrimHistLevel = XCRHISSR)


All_Crime_1.noNA <- na.omit(All_Crime_1)

```







## Selecting Variables

```{r code-chunk-label}

# Removing places outside of US
All_Crime_1 <- All_Crime_1 %>%
  filter(CIRCDIST != 69 & CIRCDIST != 74 & CIRCDIST != 5 & CIRCDIST != 18)
# Goes from 613411 obs to 602656

## Removing non-Citizens

All_Crime_1 <- All_Crime_1 %>%
  filter(NEWCIT == 0)
# Goes from 602656 to 325455

# Removing people under 18

All_Crime_1 <- All_Crime_1 %>%
  filter(AGE >= 18)
# From 325455 to 352346

```




## Offense Type
### Violent, Drug, White Collar, Other

## Categorization from Demuth and Doerner 
Violent = Manslaughter, Kidnapping/hostage, Sexual Abuse, Assault, Bank Robbery / Other Robbery

Drug = Drug Trafficking, Drug Communication, Drug Simple Possession

White Collar =  Fraud, Embezzlement, Forgery/Counterfeiting, Bribery, Tax Offenses, Money Laundering

Other = Arson, Firearms, Burglary/Breaking&Entering, Auto theft, Larceny, Racketeering/extortion, Gambling/lottery, Civil rights offenses, Immigration, Pornography/prostitution, Offenses in prison, Administration of justice-related, Environmental, game, fish, and wildlife offenses, National defense offenses, Antitrust violations, Food and drug offenses, Traffic violations and other offenses



```{r}

All_Crime_1$Violent <- ifelse(All_Crime_1$OFFGUIDE == 4 | All_Crime_1$OFFGUIDE == 19 | All_Crime_1$OFFGUIDE == 20 | All_Crime_1$OFFGUIDE == 22 | All_Crime_1$OFFGUIDE == 26 | All_Crime_1$OFFGUIDE == 27, 1, 0)

All_Crime_1$Drug = ifelse(All_Crime_1$OFFGUIDE == 9 | All_Crime_1$OFFGUIDE == 10, 1, 0)

All_Crime_1$WhiteCollar <- ifelse(All_Crime_1$OFFGUIDE == 16 | All_Crime_1$OFFGUIDE == 15 | All_Crime_1$OFFGUIDE == 5 | All_Crime_1$OFFGUIDE == 29 | All_Crime_1$OFFGUIDE == 21, 1, 0)

All_Crime_1$OtherCrime <-  ifelse(All_Crime_1$OFFGUIDE == 1 | All_Crime_1$OFFGUIDE == 2 | All_Crime_1$OFFGUIDE == 3 | All_Crime_1$OFFGUIDE == 6 | All_Crime_1$OFFGUIDE == 7 | All_Crime_1$OFFGUIDE == 8 | All_Crime_1$OFFGUIDE == 11 | All_Crime_1$OFFGUIDE == 12 | All_Crime_1$OFFGUIDE == 13 | All_Crime_1$OFFGUIDE == 14 | All_Crime_1$OFFGUIDE == 17 | All_Crime_1$OFFGUIDE == 18 | All_Crime_1$OFFGUIDE == 23 | All_Crime_1$OFFGUIDE == 24 | All_Crime_1$OFFGUIDE== 25 | All_Crime_1$OFFGUIDE == 28 | All_Crime_1$OFFGUIDE == 30, 1, 0)


# Think this was already done but doing again just in case
All_Crime_1 <- All_Crime_1 %>%
  filter(CIRCDIST != 69 & CIRCDIST != 74 & CIRCDIST != 5 & CIRCDIST != 18)

All_Crime_1 <- All_Crime_1 %>%
  filter(AGE >= 18)

All_Crime_1.noNA <- na.omit(All_Crime_1)

################# Making datasets for Crime Categorization ###############


Violent_Crime <- All_Crime_1 %>%
  filter(Violent == 1)

Drug_Crime <- All_Crime_1 %>%
  filter(Drug == 1)

WhiteCollar_Crime <- All_Crime_1 %>%
  filter(WhiteCollar == 1)

Other_Crime <- All_Crime_1 %>%
  filter(OtherCrime == 1)



```
...

