---
title: "Regression Models"
author: "Emily Blue"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(dplyr)
```


####### CATEGORIZED CRIME AND DECISION TO INCARCERATE MODELS #########################

# 0 = No Prison/Probation (Fine Only)
# 1 = Prison Only (No Alternatives)
# 2 = Prison + Confinement Conditions(Alternatives, Including Zone CSplit Sentences)
# 3 = Probation + Confinement Conditions (Alternatives)
# 4 = Probation Only

```{r}

table(All_Crime_1$SENTIMP)

All_Crime_1$Prison <- ifelse(All_Crime_1$SENTIMP == 1 | All_Crime_1$SENTIMP == 2 , 1, 0)

table(All_Crime_1$Prison)
290536 + 16573 
2177 + 11936 + 31117
# looks good

All_Crime_1.noNA <- na.omit(All_Crime_1)

table(Violent_Crime$Prison)

# Violent Crime Prison
Violent_Prison_Model <- glm(Prison ~ MONSEX + AGE + White + Hispanic + Other + HSgrad + SomeCollege + CollegeGrad + Northeast + West + Midwest + Dependents + WEAPON + CRIMHIST + OffenseLevel + NOCOUNTS + Plea + Released + Bail_Bond, data = Violent_Crime, family = "binomial")


summary(Violent_Prison_Model)
exp(coef(Violent_Prison_Model)) # Call for log odds 


# Drug Crime Prison
Drug_Prison_Model <- glm(Prison ~ MONSEX + AGE + White + Hispanic + Other + HSgrad + SomeCollege + CollegeGrad + Northeast + West + Midwest + Dependents + WEAPON +  CRIMHIST + OffenseLevel + NOCOUNTS + Plea + Released + Bail_Bond, data = Drug_Crime, family = "binomial")

summary(Drug_Prison_Model)
exp(coef(Drug_Prison_Model))

# White Collar Crime Prison
WhiteCollar_Prison_Model <- glm(Prison ~ MONSEX + AGE + White + Hispanic + Other + HSgrad + SomeCollege + CollegeGrad + Northeast + West + Midwest + Dependents + WEAPON  + CRIMHIST + OffenseLevel + NOCOUNTS + Plea + Released + Bail_Bond, data = WhiteCollar_Crime, family = "binomial")

summary(WhiteCollar_Prison_Model)
exp(coef(WhiteCollar_Prison_Model))

# Other Crime Prison

options(scipen = 0)

OtherCrime_Prison_Model <- glm(Prison ~ MONSEX + AGE + White + Hispanic + Other + HSgrad + SomeCollege + CollegeGrad + Northeast + West + Midwest + Dependents + WEAPON  + CRIMHIST + OffenseLevel + NOCOUNTS + Plea + Released + Bail_Bond, data = Other_Crime, family = "binomial")


summary(OtherCrime_Prison_Model)
exp(coef(OtherCrime_Prison_Model))

```


## Sentence Length Linear Regression Model

## Violent Crime, Drug Crime, White-Collar Crime, and Other Crime

```{rr}

# Violent Crime
Violent_Model <- lm(SENSPCAP ~ MONSEX + AGE + White + Hispanic + Other + HSgrad + SomeCollege + CollegeGrad + Northeast + West + Midwest + Dependents + WEAPON + GLMIN + CRIMHIST + OffenseLevel + NOCOUNTS + Plea + Released + Bail_Bond, data = Violent_Crime)

summary(Violent_Model)

# Drug Crime
Drug_Model <- lm(SENSPCAP ~ MONSEX + AGE + White + Hispanic + Other + HSgrad + SomeCollege + CollegeGrad + Northeast + West + Midwest + Dependents + WEAPON + GLMIN + CRIMHIST + OffenseLevel + NOCOUNTS + Plea + Released + Bail_Bond, data = Drug_Crime)

summary(Drug_Model)

# White Collar Crime
WhiteCollar_Model <- lm(SENSPCAP ~ MONSEX + AGE + White + Hispanic + Other + HSgrad + SomeCollege + CollegeGrad + Northeast + West + Midwest + Dependents + WEAPON + GLMIN + CRIMHIST + OffenseLevel + NOCOUNTS + Plea + Released + Bail_Bond, data = WhiteCollar_Crime)

summary(WhiteCollar_Model)

# Other Crime

OtherCrime_Model <- lm(SENSPCAP ~ MONSEX + AGE + White + Hispanic + Other + HSgrad + SomeCollege + CollegeGrad + Northeast + West + Midwest + Dependents + WEAPON + GLMIN + CRIMHIST + OffenseLevel + NOCOUNTS + Plea + Released + Bail_Bond, data = Other_Crime)

summary(OtherCrime_Model)

```
...

